---
title: "AVT - pilot"
author: "Ana Guerberof Arenas"
date: "Generated on: `r date()`"
output:
  html_document:
    code_folding: show
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
---


# Load Libraries and Data
```{r}
library(ggplot2)
library(tidyverse)
library(viridis)
library(hrbrthemes)
library(effsize) # for effect size of wilcox test
library(car) # leveneTest
library("ggpubr")
library(psych)
library(ltm)
library(lme4)
library(FSA)
library(DescTools)
library(broom)

df <- read.csv("AVT+Engagement+pilot+anonymised.csv")
```

# Preprocess Data

```{r}

# reading condition A = PE, B = MT, C = HT
table(df$Condition) # show number of responses per condition


# gender 1 = female, 2 = male, 3 = non-binary, 4 = prefer not to say
table(df$Q1.1)

# age 2 = 18-24, 3= 25-34,  4= 35-44, 5 = 45-54, 6 = 55-64, 7= 65-74, 8= 75-84, 9= 85 or older
df$Q1.2 <- factor(df$Q1.2)
table(df$Q1.2)
#table(df$Q1.2, df$UserLanguage)

#Mother Tongue  1 is English, 2 Spanish, 3 English and Spanish, 4 Another Language
table(df$Q1.6) 
table(df$Q1.6, df$Condition) 
# studies 1 = less than secondary school, 2 = Secondary School, 3= Some college education, 4 = BA, 5 = Master, 6 = Professional Degree, 7= Doctorate)
table(df$Q1.4)


# profession 1, 2, 3, 4, 5 are related to language, 6 is others.
table(df$Q1.5)
df$prof <- NULL
df$prof[df$Q1.5==6] <- 6
df$prof[is.na(df$prof)==TRUE & is.na(df$Q1.5)==FALSE & df$Q1.5 != ""] <- 1
df$prof <- as.factor(df$prof)
table(df$prof)
# 1 is professions related to languages and 6 is others)

# Level of Spanish 1= No knowledge, 2= A little, 3= A moderate amount, 4= Very good knowledge, 5= Bilingual level
table(df$Q1.7)

# Level of English 1= No knowledge, 2= A little, 3= A moderate amount, 4= Very good knowledge, 5= Bilingual level
table(df$Q1.8)

# Watch subtitles How often do you watched programmes with subtitles in the last 24 months?  1= Never, 2= Once every three months, 3= Once a month, 4= Once or twice per week, 5= Daily)
table(df$Q1.9)


# How much do you enjoy watching tv programmes with subtitles  1 = dislike a great deal, 2 = dislike somewhat, 3 = Neither like or dislike, 4= Like somewhat, 5 = Like a lot")
table(df$Q1.10) 

# How many subcriptions to streaming platforms do you have? 1 = None at all, 2 = One, 3 = Between two and three, 4 = Between four and five, 5 = More than 5
table(df$Q1.12)


```

# Narrative understanding
```{r}
df$n_underst <- (df$Q3.1 + df$Q3.2 + df$Q3.3)/3

tapply(df$Q3.1, df$Condition, mean) # At points, I had a hard time making sense of what was going on in the story
tapply(df$Q3.2, df$Condition, mean) # My understanding of the characters is unclear.
tapply(df$Q3.3, df$Condition, mean) # I had a hard time recognizing the thread of the story.

ggplot(data =df,mapping = aes(x = Condition,y = n_underst))+geom_boxplot(aes(fill=Condition), show.legend = FALSE)+
    ggtitle("All") +
    xlab("Translation modality")+
    scale_x_discrete(labels=c("PE","MT","HT")) +
    ylab("Narrative understanding")

kruskal.test(n_underst ~ Condition, data = df)
dunnTest(n_underst ~ Condition, data = df, method="bonferroni")

summary(lm(df$n_underst ~ df$Condition))
```

# Attentional Focus
```{r}
df$att_focus <- (df$Q3.4 + df$Q3.5 + df$Q3.6)/3

tapply(df$Q3.4, df$Condition, mean) # I found my mind wandering while reading the story.
tapply(df$Q3.5, df$Condition, mean) # While reading, I found myself thinking about other things.
tapply(df$Q3.6, df$Condition, mean) # I had a hard time keeping my mind on the story.

ggplot(data =df,mapping = aes(x = Condition,y = att_focus))+geom_boxplot(aes(fill=Condition), show.legend = FALSE)+
     ggtitle("All") +
    xlab("Translation modality")+
    scale_x_discrete(labels=c("PE","MT","HT")) +
    ylab("Attentional Focus") 


kruskal.test(att_focus ~ Condition, data = df)
dunnTest(att_focus ~ Condition, data = df, method="bonferroni")

summary(lm(df$att_focus ~ df$Condition)) 

```

# Narrative presence
```{r}
df$n_presence <- (df$Q3.7 + df$Q3.8 + df$Q3.9)/3

tapply(df$Q3.7, df$Condition, mean) #During the reading, my body was in the room, but my mind was inside the world created by the story.
tapply(df$Q3.8, df$Condition, mean) #The story created a new world, and then that world suddenly disappeared when the story ended.
tapply(df$Q3.9, df$Condition, mean) #At times during the reading, I was closer to the situation described in the story than the realities of here-and-now

ggplot(data =df,mapping = aes(x = Condition,y = n_presence))+geom_boxplot(aes(fill=Condition), show.legend = FALSE)+
     ggtitle("All") +
    xlab("Translation modality")+
    scale_x_discrete(labels=c("PE","MT","HT")) +
    ylab("Narrative presence")

kruskal.test(n_presence ~ Condition, data = df)
dunnTest(n_presence ~ Condition, data = df, method="bonferroni")

leveneTest(df$n_presence ~ df$Condition)
summary(lm(df$n_presence ~ df$Condition)) # B and C dec, neither sig
summary(aov(df$n_presence ~ df$Condition))
```

# Emotional engagement
```{r}
df$e_engag <- (df$Q3.10 + df$Q3.11 + df$Q3.12)/3

tapply(df$Q3.10, df$Condition, mean) #During the narrative, when a main character suffered, I felt sad.
tapply(df$Q3.11, df$Condition, mean) #The story affected me emotionally.
tapply(df$Q3.12, df$Condition, mean) #I felt sorry for some of the characters in the story.

ggplot(data =df,mapping = aes(x = Condition,y = e_engag))+geom_boxplot(aes(fill=Condition), show.legend = FALSE)+
     ggtitle("All") +
    xlab("Translation modality")+
    scale_x_discrete(labels=c("PE","MT","HT")) +
    ylab("Emotional engagement") 

kruskal.test(e_engag ~ Condition, data = df)
dunnTest(e_engag ~ Condition, data = df, method="bonferroni")


summary(lm(df$e_engag ~ df$Condition)) # B & C dec, neither sig
```

# Narrative engagement overall
```{r}

df$engagement <- (df$Q3.1 + df$Q3.2 + df$Q3.3 + df$Q3.4+ df$Q3.5+ df$Q3.6+ df$Q3.7+ df$Q3.8+ df$Q3.9+ df$Q3.10+ df$Q3.11+ df$Q3.12)/12

dataEng <- data.frame(df$Q3.1, df$Q3.2, df$Q3.3, df$Q3.4, df$Q3.5, df$Q3.6, df$Q3.7, df$Q3.8, df$Q3.9, df$Q3.10, df$Q3.11, df$Q3.12)
cronbach.alpha(dataEng, CI=TRUE)
alpha(dataEng, keys=NULL,cumulative=FALSE, title=NULL, max=10,na.rm = TRUE,
   check.keys=FALSE,n.iter=1,delete=TRUE,use="pairwise",warnings=TRUE,n.obs=NULL)

ggplot(data =df,mapping = aes(x = Condition,y = engagement))+geom_boxplot(aes(fill=Condition), show.legend = FALSE)+
     ggtitle("All") +
    xlab("Translation modality")+
    scale_x_discrete(labels=c("PE","MT","HT")) +
    ylab("Narrative engagement overall") 

#summary(lm(df$engagement ~ df$Condition)) # B & C dec, neither sig
tapply(df$engagement, df$Condition, mean)
tapply(df$engagement, df$Condition, median)

summary(lm(df$engagement ~ df$Condition)) # B & C dec, neither sig

kruskal.test(engagement ~ Condition, data = df)
dunnTest(engagement ~ Condition, data = df, method="bonferroni")

```


# Translation Reception
```{r}

# Cronbach Alpha
dataTrans <-data.frame(df$Q4.1, df$Q4.2, df$Q4.3, df$Q4.5, df$Q4.7)
cronbach.alpha(dataTrans, CI=TRUE, na.rm = TRUE) 
alpha(dataTrans, keys=NULL,cumulative=FALSE, title=NULL, max=10,na.rm = TRUE,
   check.keys=FALSE,n.iter=1,delete=TRUE,use="pairwise",warnings=TRUE,n.obs=NULL)

df$t_rep <- (df$Q4.1 + df$Q4.2 + df$Q4.3 + df$Q4.5 + df$Q4.7)/5
tapply(df$t_rep, df$Condition, mean)


tapply(df$Q4.1, df$Condition, mean) # How easy was the text to understand?
tapply(df$Q4.2, df$Condition, mean) # I thought the text was very well written.
tapply(df$Q4.3, df$Condition, mean) #  I found words, sentences or paragraphs that were difficult to understand. (a higher value indicates that there were no difficulties)
tapply(df$Q4.5, df$Condition, mean) # I found words, sentences or paragraphs that I specially liked. (a higher value means that there were more objects liked)
tapply(df$Q4.7, df$Condition, mean) # I was conscious that I was reading a translation.(a higher value indicates no consciousness)

ggplot(data =df,mapping = aes(x = Condition,y = t_rep))+geom_boxplot(aes(fill=Condition), show.legend = FALSE)+
     ggtitle("All") +
    xlab("Translation modality")+
    scale_x_discrete(labels=c("PE","MT","HT")) +
    ylab("Translation Reception") 


summary(lm(df$t_rep ~ df$Condition)) # =
summary(lm(df$t_rep ~ df$Condition))


kruskal.test(t_rep ~ Condition, data = df)
dunnTest(t_rep ~ Condition, data = df, method="bonferroni")


```

# Enjoyment

```{r}
# 
df$enjoyment <- (df$Q5.1 + df$Q5.2)/2

# 
tapply(df$Q5.1, df$Condition, mean) # How much did you enjoy reading the text?
tapply(df$Q5.2, df$Condition, mean) # Would you recommend this text to a friend?

tapply(df$enjoyment, df$Condition, mean)
tapply(df$enjoyment, df$Condition, median)

dataEnjoy <-data.frame(df$Q5.1, df$Q5.2)
newdataEnjoy <- na.omit(dataEnjoy)
cronbach.alpha(newdataEnjoy, CI=TRUE)
alpha(newdataEnjoy, keys=NULL,cumulative=FALSE, title=NULL, max=10,na.rm = TRUE,
   check.keys=FALSE,n.iter=1,delete=TRUE,use="pairwise",warnings=TRUE,n.obs=NULL)


ggplot(data =df,mapping = aes(x = Condition,y = enjoyment))+geom_boxplot(aes(fill=Condition), show.legend = FALSE)+
     ggtitle("All") +
    xlab("Translation modality")+
    scale_x_discrete(labels=c("PE","MT","HT")) +
    ylab("Enjoyment")

ggplot(data =df,mapping = aes(x = Condition,y = df$SC8))+geom_boxplot(aes(fill=Condition), show.legend = FALSE)+
     ggtitle("All") +
    xlab("Translation modality")+
    scale_x_discrete(labels=c("PE","MT","HT")) +
    ylab("Enjoyment") 

summary(lm(df$enjoyment ~ df$Condition))

kruskal.test(enjoyment ~ Condition, data = df)
dunnTest(enjoyment ~ Condition, data = df, method="bonferroni")

```


# Comprehension Questions
```{r}
ggplot(data =df,mapping = aes(x = Condition,y = CorrectAnswers))+geom_boxplot(aes(fill=Condition), show.legend = FALSE)+
     ggtitle("All") +
    xlab("Translation modality")+
    scale_x_discrete(labels=c("PE","MT","HT")) +
    ylab("Comprehension") 

# means (may be more appropriate since we've ordinal data)
tapply(df$CorrectAnswers, df$Condition, mean)

summary(lm(df$CorrectAnswers ~ df$Condition)) # B and C dec, neither sig (before both sig)
```

# AVT frequency
```{r}
df$viewingpatterns <- (df$Q1.9 + df$Q1.10)/2
# the scale here was 1 to 5, higher values indicate more wathing programmes with subtitles

tapply(df$viewingpatterns, df$Condition, mean)

dataRead <-data.frame(df$Q1.9, df$Q1.10)
cronbach.alpha(dataRead, CI=TRUE)
alpha(dataRead, keys=NULL,cumulative=FALSE, title=NULL, max=10,na.rm = TRUE,
   check.keys=FALSE,n.iter=1,delete=TRUE,use="pairwise",warnings=TRUE,n.obs=NULL)

ggplot(data =df,mapping = aes(x = Condition,y = viewingpatterns))+geom_boxplot(aes(fill=Condition), show.legend = FALSE)+
     ggtitle("All") +
    xlab("Translation modality")+
    scale_x_discrete(labels=c("PE","MT","HT")) +
    ylab("Viewing patterns") 

summary(lm(df$viewingpatterns ~ df$Condition))

kruskal.test(df$viewingpatterns ~ Condition, data = df)
dunnTest(df$viewingpatterns ~ Condition, data = df, method="bonferroni")


```

# Duration (by condition)

The only duration we'll probably keep is by condition, as that variable is the one of interest.

Below, there's also duration by gender and other variables. Probably we will not keep those.

```{r}
ggplot(data =df,mapping = aes(x = Condition,y = Duration..in.seconds.))+geom_boxplot(aes(fill=Condition), show.legend = FALSE)+
     ggtitle("All") +
    xlab("Translation modality")+
    scale_x_discrete(labels=c("PE","MT","HT")) +
    ylab("Duration in seconds") 

df_duration <- df[which(df$Duration..in.seconds. < 10000),] # remove outliers (very slow ones): 8 out of 88 (3 HT, 4 PE, 1 MT)
table(df$Condition)
table(df_duration$Condition)

boxplot(df_duration$Duration..in.seconds. ~ df_duration$Condition, ylab="Duration (seconds)")

df_duration2 <- df_duration[which(df_duration$Duration..in.seconds. < 3800),] # remove outliers (very slow ones): 7 out of 80 (2 HT, 2 PE, 3 MT)
table(df_duration2$Condition)

boxplot(df_duration2$Duration..in.seconds. ~ df_duration2$Condition, ylab="Duration (seconds)")

tapply(df_duration2$Duration..in.seconds., df_duration2$Condition, mean)
summary(lm(df_duration2$Duration..in.seconds. ~ df_duration2$Condition)) # =, B&C dec, no sig
```

## Duration (by device)
```{r}
# 1 = Computer, 2 = Table, 3 = Mobile, 4 = Other
boxplot(df_duration2$Duration..in.seconds. ~ df_duration2$Q6.1, ylab="Duration (seconds)")
tapply(df_duration2$Duration..in.seconds., df_duration2$Q6.1, mean)
summary(lm(df_duration2$Duration..in.seconds. ~ df_duration2$Q6.1)) # no sig
```

## Duration (by gender)
```{r}
#1 = female, 2 = male, 3 = non-binary, 4 = prefer not to say

boxplot(df_duration2$Duration..in.seconds. ~ df_duration2$Q1.1, ylab="Duration (seconds)")
tapply(df_duration2$Duration..in.seconds., df_duration2$Q1.1, mean)
summary(lm(df_duration2$Duration..in.seconds. ~ df_duration2$Q1.1)) # no sig
```

## Duration (by age)
```{r}
#2 = 18-24, 3= 25-34,  4= 35-44, 5 = 45-54, 6 = 55-64, 7= 65-74, 8= 75-84, 9= 85 or older
boxplot(df_duration2$Duration..in.seconds. ~ df_duration2$Q1.2, ylab="Duration (seconds)")
tapply(df_duration2$Duration..in.seconds., df_duration2$Q1.2, mean)
summary(lm(df_duration2$Duration..in.seconds. ~ df_duration2$Q1.2)) # no sig
```

## Duration (by profession)
```{r}
#1, 2, 3, 4, 5 = related to language; 6 = unrelated to language
boxplot(df_duration2$Duration..in.seconds. ~ df_duration2$Q1.5, ylab="Duration (seconds)")
tapply(df_duration2$Duration..in.seconds., df_duration2$Q1.5, mean)
summary(lm(df_duration2$Duration..in.seconds. ~ df_duration2$Q1.4)) # unrelated_lang slower but no sig
```

## Duration (by native language)
```{r}
boxplot(df_duration2$Duration..in.seconds. ~ df_duration2$Q1.6, ylab="Duration (seconds)")
tapply(df_duration2$Duration..in.seconds., df_duration2$Q1.6, mean)
summary(lm(df_duration2$Duration..in.seconds. ~ df_duration2$Q1.6)) # bilinguals faster but no sig
```


# Any paragraph liked?

```{r}

table(df$Q4.5, df$Condition) 
tapply(df$Q4.5, df$Condition, mean)
# Higher value indicates more like
```

# Any paragraph difficult?

```{r}
table(df$Q4.3, df$Condition) # I found words or sentences that were difficult to understand.
tapply(df$Q4.3, df$Condition, mean)
# Higher value indicates less difficulty.

```

# Correlations between reading patterns & narrative engagement, enjoyment and translation reception

```{r}
#cor.test(x, y, method=c("pearson", "kendall", "spearman"))
#SC8 reading patterns, SC9 enjoyment, SC3 translation reception, SC10 narrativement engagement
#age and gender, profession?

ggqqplot(df$SC7, ylab = "reading patterns")
ggqqplot(df$SC8, ylab = "enjoyment")
shapiro.test(df$SC7) # => p = 0.1229
shapiro.test(df$SC8) # => p = 0.1229
cor.test(df$SC8, df$SC7, method=c("spearman"))
cor.test(df$SC8, df$SC7, method=c("kendall"))
ggscatter(df, x = "SC7", y = "SC8", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "Reading patterns", ylab = "Enjoyment")

cor.test(df$SC2, df$SC7, method=c("kendall"))
ggscatter(df, x = "SC7", y = "SC2", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "Reading patterns", ylab = "Translation")

cor.test(df$SC9, df$SC7, method=c("kendall"))
ggscatter(df, x = "SC7", y = "SC9", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "Reading patterns", ylab = "Narrative Engagement")


ggqqplot(df$SC7, ylab = "enjoyment")
ggqqplot(df$SC2, ylab = "translation")#SC8 reading patterns, SC9 enjoyment, SC3 translation reception, SC10 narrativement engagement
shapiro.test(df$SC7)
shapiro.test(df$SC2)
cor.test(df$SC2, df$SC7, method=c("kendall"))
ggscatter(df, x = "SC2", y = "SC7", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "translation", ylab = "Enjoyment")

ggqqplot(df$SC9, ylab = "narrative engagement")
ggqqplot(df$SC2, ylab = "translation")
shapiro.test(df$SC9)
shapiro.test(df$SC2)
cor.test(df$SC2, df$SC9, method=c("kendall"))
ggscatter(df, x = "SC9", y = "SC2", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "translation", ylab = "narrative engagement")


```


